Supplementary material

### 2021-06-23 submission/supplement.rmd
write interaction results

```{r test, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_interactions.png"))
```

```{r test2, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/discrimination_interactions.png"))
```

```{r test4, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/calibration_interactions.png"))
```

>>>>

When we considered a set of 4 true linear treatment-covariate interactions the
model containing a linear interaction with the prognostic index had the lowest
median RMSE. We observed an increasing trend in prediction errors with
increasing interaction intensity (Figure \@ref(fig:rmseInteractions)). The
model with restricted cubic spline smoothing (3 knots) had very comparable
performance to the linear interaction model. Increasing the flexibility of the
smooth methods resulted in increasing median RMSE. These results may be
explained by the fact that the interactions considered were linear, thus
favoring the linear interaction model. More flexible approaches may be better
suited for higher-order treatment-covariate interactions. Finally, the adaptive
approach had adequate performance under all scenarios, resembling the
performance of the best-performing approach every time.

```{r rmseInteractions, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_interactions.png"))
```

The constant treatment effects model, the linear interaction model and the model
with RCS smoothing (3 knots) had the highest c-for-benefit across all scenarios
(Figrue \@ref(fig:discriminationInteractions)). RCS smoothing with 4 or 5 knots
did not improve performance. On the contrary, we observed an increasing trend in
c-for-benefit variability, as was the case in the main text. The adaptive
apprach again had statisfactory performance.

```{r discriminationInteractions, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/discrimination_interactions.png"))
```

Despite the very similar performance in terms of prediction errors, the linear
interaction model resulted in better-calibrated benefit predictions compared to
the rest of the methods (Figure \@ref(fig:calibrationInteractions)). The constant
treatment effects model had the highest median ICI-for-benefit across all
scenario settings, which became more pornounced with increasing
treatment-covariate interaction intensity.

```{r calibrationInteractions, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/calibration_interactions.png"))
```
